---
title: "Model Card: your model title"
date: '`r Sys.Date()`'
output: 
  html_document
params:
    board: !r pins::board_connect(auth = "envvar", server = "https://pub.vetiver.posit.team/")
    name: bensoltoff/seattle-housing-rf
    version: NULL
---

```{r setup, include=FALSE}
library(tidyverse)
library(vetiver)
library(pins)
library(yardstick)
knitr::opts_chunk$set(echo = FALSE)
v <- vetiver_pin_read(params$board, params$name, version = params$version)
v_meta <- pin_meta(params$board, params$name)
theme_set(theme_light())

# get original data
library(tidymodels)
library(arrow)
set.seed(123)

path <- here::here("data", "housing.parquet")
housing <- read_parquet(path)

set.seed(123)
housing_split <- housing |>
  mutate(price = log10(price)) |>
  initial_split(prop = 0.8)
housing_train <- training(housing_split)
housing_test <- testing(housing_split)
```

A [model card](https://doi.org/10.1145/3287560.3287596) provides brief, transparent, responsible reporting for a trained machine learning model.

## Model details

- Developed by PERSON AND/OR TEAM
- `r cli::pluralize("{v$description} using {ncol(v$prototype)} feature{?s}")`
- More details about how model was developed and what it is predicting
- More details on feature engineering and/or data preprocessing for model
- Version `r v$metadata$version` of this model was published at `r v_meta$created`
- Citation and/or license details for the model
- If you have questions about this model, please contact PERSON@ORG.ORG

## Intended use

- The primary intended uses of this model are ...
- The primary intended users of this model are ...
- Some use cases are out of scope for this model, such as ...

## Important aspects/factors

- Aspects or factors (demographic, environmental, technical) that are relevant to the context of this model are ...
- In evaluating this model, we examined aspects such as ...

## Metrics

- The metrics used to evaluate this model are ...
- These metrics are computed via ...
- We chose these metrics because ...

## Training data & evaluation data

- The training dataset for this model was ...
- The training dataset for this model has the "prototype" or signature:

    ```{r}
    glimpse(v$prototype)
    ```

- The evaluation dataset used in this model card is ...
- We chose this evaluation data because ...

```{r}
## EVALUATION DATA:

skimr::skim(housing_test)

## consider using a package like skimr or DataExplorer for automated 
## presentation of evaluation data characteristics
```


## Quantitative analyses {.tabset}

```{r}
## compute predictions for your evaluation data
## load packages needed for prediction:
library(parsnip)
library(workflows)
preds <- augment(v, housing_test)
```


### Overall model performance

```{r}
preds %>%
    metrics(price, .pred)
```

### Disaggregated model performance

```{r}
preds %>%
    group_by(waterfront) %>%
    metrics(price, .pred)
```

### Visualize model performance

```{r, fig.height=3}
preds %>%
    ggplot(aes(price, .pred, color = waterfront)) +
    geom_abline(slope = 1, lty = 2, color = "gray60", size = 1.2) +
    geom_point(alpha = 0.5, show.legend = FALSE) +
    facet_wrap(vars(waterfront))
```

### Make a custom plot

```{r}
preds %>%
    mutate(.resid = price - .pred) %>%
    ggplot(aes(long, lat, color = .resid)) +
    geom_point(alpha = 0.8) +
    scale_color_gradient2() +
    coord_fixed()
```


## Ethical considerations

- We considered ...

## Caveats & recommendations

- This model does ...
- This model does not ...
- We recommend ...



